---
title: "D.C. Airbnb Hunt"
author: "Foo Fivers"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

## D.C. Airbnb Hunt

For this project, Team Five has been propositioned by a visiting friend to recommend a neighborhood in DC that offers the best Airbnb deals. To provide an informed suggestion, the team will be using listing data from Airbnbs in DC to answer the question “What DC neighborhood offers Airbnb listings with the highest ratings at the lowest price?”. The team will provide an overall neighborhood suggestion for where to book the best Airbnb deal in DC as well as by type (entire home, private room, etc) and budget. . This data will come from `Inside Airbnb` , an open-source data tool providing web scraped Airbnb listing information by city.

```{r, echo = FALSE, results = 'hide', message = FALSE}
library(tidyverse)
library(dplyr)
library(knitr)
library(kableExtra)
library(readr)
```
## Data Preprocessing

```{r}
df <- read.csv('listings_detailed.csv')
df <- df %>% 
  select(id, name, host_is_superhost, host_listings_count, neighbourhood_cleansed, latitude, longitude, room_type, bedrooms, beds, amenities, price, availability_60, number_of_reviews, review_scores_rating, reviews_per_month) %>% 
  mutate(price = as.numeric(parse_number(price)),
         neighbourhood_cleansed = as.factor(neighbourhood_cleansed),
         room_type = as.factor(room_type)) %>%
  rename(neighbourhood = neighbourhood_cleansed)
glimpse(df)
```

<!--

(ricky)
- Description: Column name, meaning, values, type
- Overview
- Price distribution - histogram + qq plot
- Neighbourhoods - barchart?

(atharva)
- Room types
- review score distribution
- reviews_per_month distribution

EDA (adrienne)
- whatever she has done already

(maaz)
- correlation plot
- anova test
- name keyword vs price and review
-->


