---
title: "D.C. Airbnb Hunt"
author: "Foo Fivers"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
    toc: true
    number_sections: true
    

---

# Introduction

For this project, Team Five has been propositioned by a visiting friend to recommend a neighborhood in DC that offers the best Airbnb deals. To provide an informed suggestion, the team will be using listing data from Airbnbs in DC to answer the question “What DC neighborhood offers Airbnb listings with the highest ratings at the lowest price?”. The team will provide an overall neighborhood suggestion for where to book the best Airbnb deal in DC as well as by type (entire home, private room, etc) and budget. . This data will come from `Inside Airbnb` , an open-source data tool providing web scraped Airbnb listing information by city.

```{r, echo = FALSE, results = 'hide', message = FALSE}
library(tidyverse)
library(dplyr)
library(knitr)
library(kableExtra)
library(readr)
library(plyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(leaflet)
library(tidytext)
library(stringr)
library(wordcloud)
library(ezids)
knitr::opts_chunk$set(warning = FALSE)
```

# Data Preprocessing


```{r}
df <- read.csv('listings_detailed.csv')
#nrow(df)
#print('')
colnames(df)

df <- df %>% 
  dplyr::select(id, name, host_is_superhost, host_listings_count, neighbourhood_cleansed, latitude, longitude, room_type, bedrooms, beds, amenities, price, availability_60, number_of_reviews, review_scores_rating,  review_scores_accuracy, review_scores_cleanliness,
            review_scores_checkin, review_scores_communication, review_scores_location, review_scores_value, reviews_per_month) %>% 
  dplyr::mutate(price = as.numeric(parse_number(price)),
         neighbourhood_cleansed = as.factor(neighbourhood_cleansed),
         amenities = lengths(strsplit((str_sub(df$amenities, 2, -2)), ",")),
         room_type = as.factor(room_type),
         bedrooms = as.factor(bedrooms)) %>%
  dplyr::rename(neighbourhood = neighbourhood_cleansed)


df = na.omit(df)


```
To begin the AirBnB search for our friend, we must prepare our data for analysis. With this dataset we will select the `r ncol(df)` variables that will help us answer this question. We will also make sure all of our variables are in the appropriate form, rename necessary columns and remove na values. With this cleansing our dataset now has `r nrow(df)` airbnb units for analysis. 

# Data Summary
```{r}
glimpse(df)
```

# Descriptive statistics

## Price
```{r, fig.show='hide'}
Price_No_Outlier = outlierKD2(df, price, rm=TRUE)
```

```{r}
par(mfrow = c(1,2))
hist(Price_No_Outlier$price, main = 'Histogram of Price', xlim = c(0,350))
qqnorm(Price_No_Outlier$price, main="Q-Q plot of Price")
qqline(Price_No_Outlier$price)
```

## Reviews

```{r, fig.show='hide'}
Number_of_Reviews_No_Outlier = outlierKD2(df, number_of_reviews, rm=TRUE)
```

```{r}
par(mfrow = c(1,2))
hist(Number_of_Reviews_No_Outlier$number_of_reviews, main = 'Histogram of Number of Reviews', xlim = c(0,200))
qqnorm(Number_of_Reviews_No_Outlier$number_of_reviews, main="Q-Q plot of Number of Reviews")
qqline(Number_of_Reviews_No_Outlier$number_of_reviews)
```

## Amenities

```{r, fig.show='hide'}
Number_of_Amenities_No_Outlier = outlierKD2(df, amenities, rm=TRUE)
```

```{r}
par(mfrow = c(1,2))
hist(Number_of_Amenities_No_Outlier$amenities, main = 'Histogram of Amenities', xlim = c(0,65))
qqnorm(Number_of_Amenities_No_Outlier$amenities, main="Q-Q plot of Amenities")
qqline(Number_of_Amenities_No_Outlier$amenities)
```

# Exploratory Data Analysis

## Room types

To better understand the AirBnB market in DC, we will first look at the split out of room types and their proportions in the district. This pie chart shows us that there are four types of rooms offered from AirBnB in DC and that Entire home/apt makes up the greatest proportion of these units. 

```{r}

d = as.data.frame(table(df$room_type))

group.colors = c("Entire home/apt" ="#51c5ed","Shared room"="#C3EB78","Private room"="#ff616f","Hotel room"="#3D348B")

ggplot(d, aes(y = Freq, x = "", fill = Var1)) + geom_bar(width=3, stat = "identity")+ coord_polar("y", start = 0)  + labs(title = "DC AirBnB Pie Chart of Room Types", x = "", y = "")+ 
  theme(
        legend.title=element_text(size=9),
        plot.title = element_text(color="black", face="bold", size=16, hjust=0),
        panel.grid.major = element_line(colour = "grey90", size = 0.2),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = 'white'),legend.position="right")+
        scale_fill_manual(values=group.colors)+
        labs(fill = "Room Type")

```

## Neighorhood and Room Type

We will now split this out by neighborhood to see where there is the greatest selection of AirBnB units in the district. 

```{r}

#create column for neighborhood name in visualizations
df$neighbourhood_short <- str_sub(df$neighbourhood,1,15)

#add in column for frequency of listings
df_freq <- merge(df, data.frame(table(neighbourhood = df$neighbourhood)), by = c("neighbourhood"))


#create barplot of airbnb frequency by DC neighborhoods
ggplot(df_freq,aes(x=reorder(neighbourhood_short, neighbourhood_short, function(x)-length(x))))+geom_bar(aes(fill = room_type), alpha=.9)+ theme(axis.text.x = element_text(angle = 90),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        legend.title=element_text(size=9),
        plot.title = element_text(color="black", face="bold", size=16, hjust=0),
        panel.grid.major = element_line(colour = "grey90", size = 0.2),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = 'white'),legend.position="top")+
        scale_fill_manual(values=group.colors)+
        labs(fill = "Room Type", x="Neighborhood", y="# of AirBnBs Listed")+
        ggtitle("Frequency of AirBnBs by Neighborhood and Room Type") 

#v = as.data.frame(table(df$neighbourhood))
#v1 = v %>% slice(1:20)

#v2 = v %>% slice(21:50)

#par(mfrow = c(1,2))

#barplot(v1$Freq, main = "Barplot of Neighborhood Counts P1", ylab = "Count",  width = 5, names.arg = v1$Var1, las = 2, cex.names=0.6, col = 'darkred')

#barplot(v2$Freq, main = "Barplot of Neighborhood Counts P2", ylab = "Count",  width = 5, names.arg = v2$Var1, las = 2, cex.names=0.6, col = 'lightblue')

```


## Price and room type
We are not sure what room type our friend is looking for. So, to allow them to understand the options, we will plot average price by room type. As we saw in the summary statistics, there is a large spread on this data. So, we will be viewing these plots zoomed in to the 0 - 95th percentile.  

```{r}

ggplot(df,aes(x=room_type, y=price))+ geom_boxplot(outlier.shape = NA ) +
coord_cartesian(ylim = quantile(df$price, c(0.0, .95)))+
  geom_jitter(width=0.15, alpha=.05, aes(colour=room_type))+
  theme(axis.text.x = element_text(angle = 90, size=7))+
  theme(axis.text.x = element_text(angle = 90),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        
        plot.title = element_text(color="black", face="bold", size=16, hjust=0),
        panel.grid.major = element_line(colour = "grey90", size = 0.2),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = 'white'),
        legend.position = "none")+
        scale_colour_manual(values=group.colors)+
        labs( x="Room Type", y="Price")+
        ggtitle("Box Plot of Price Distribution by Room Type")

```

## Reviews and room type

Now we will do the same for rating. This time we will zoom from the 1st to 100th percentile. 

```{r}

ggplot(df,aes(x=room_type, y=review_scores_rating))+ geom_boxplot(outlier.shape = NA ) +
coord_cartesian(ylim = quantile(df$review_scores_rating, c(.01, 1)))+
  geom_jitter(width=0.15, alpha=.05, aes(colour=room_type))+
  theme(axis.text.x = element_text(angle = 90, size=7))+
  theme(axis.text.x = element_text(angle = 90),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        
        plot.title = element_text(color="black", face="bold", size=16, hjust=0),
        panel.grid.major = element_line(colour = "grey90", size = 0.2),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = 'white'),
        legend.position = "none")+
        scale_colour_manual(values=group.colors)+
        labs( x="Room Type", y="Price")+
        ggtitle("Box Plot of Rating Distribution by Room Type")

```

## Amenities and room type
```{r}
price_room = df %>%
  group_by(room_type) %>%
  summarise_at(vars(price), list(price = mean))

price_room = data.frame(price_room)

price_room[order(-rank(price_room$price), decreasing = FALSE), ]%>% 
  kbl() %>%
  kable_paper("hover", full_width = F)
```

```{r}
rating_room = df %>%
  group_by(room_type) %>%
  summarise_at(vars(review_scores_rating), list(review_scores_rating = mean))

rating_room = data.frame(rating_room)
rating_room[order(-rank(rating_room$review_scores_rating), decreasing = FALSE), ]%>% 
  kbl() %>%
  kable_paper("hover", full_width = F)
```

```{r}
amenities_room = df %>%
  group_by(room_type) %>%
  summarise_at(vars(amenities), list(amenities = mean))

amenities_room = data.frame(amenities_room)

amenities_room[order(-rank(amenities_room$amenities), decreasing = FALSE), ]%>% 
  kbl() %>%
  kable_paper("hover", full_width = F)
```

## Price and neighbourhood

Now we will start to look into the neighborhoods in DC. First, we will compare price across the neighborhoods. Before we do this, we should narrow down the neighborhood options for our friend. With our initial dataset, we find there are `r n_distinct(df$neighbourhood)` DC neighborhoods we could recommend our friend look for an AirBnB. We want to make sure that our friend has a large number of AirBnBs to select from our final neighborhood selection. So, we will now only include only neighborhoods with over 200 AirBnB units listed with review and pricing data. 

```{r}
#subset data where frequency is greater than 175
df_175 <-  df_freq[ which(df_freq$Freq>175), ]
```

Our subsetted data set now has `r n_distinct(df_175$neighbourhood)` neighborhoods with `r nrow(df_175)` data points to analyze. 

We can now analyze price across neighborhoods. To better view this graph, we will be zooming in to view the 0th to 95th percentile. 

```{r}

ggplot(df_175,aes(x=neighbourhood_short, y=price))+ geom_boxplot(outlier.shape = NA ) +
coord_cartesian(ylim = quantile(df$price, c(.0, .95)))+
  geom_jitter(width=0.15, alpha=.05, aes(colour=neighbourhood_short))+
  theme(axis.text.x = element_text(angle = 90, size=7))+
  theme(axis.text.x = element_text(angle = 90),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        
        plot.title = element_text(color="black", face="bold", size=16, hjust=0),
        panel.grid.major = element_line(colour = "grey90", size = 0.2),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = 'white'),
        legend.position = "none")+
        labs( x="Room Type", y="Price")+
        ggtitle("Box Plot of Price Distribution by Neighborhood")

```

## Reviews and neighbourhood

Next we will look at rating across neighborhoods. To better view this graph, we will be zooming in to view the 3rd to 100th percentile. 

```{r}

ggplot(df_175,aes(x=neighbourhood_short, y=review_scores_rating))+ geom_boxplot(outlier.shape = NA ) +
coord_cartesian(ylim = quantile(df$review_scores_rating, c(.02, 1)))+
  geom_jitter(width=0.15, alpha=.05, aes(colour=neighbourhood_short))+
  theme(axis.text.x = element_text(angle = 90, size=7))+
  theme(axis.text.x = element_text(angle = 90),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        
        plot.title = element_text(color="black", face="bold", size=16, hjust=0),
        panel.grid.major = element_line(colour = "grey90", size = 0.2),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = 'white'),
        legend.position = "none")+
        labs( x="Room Type", y="Price")+
        ggtitle("Box Plot of Rating Distribution by Neighborhood")

```

## Amenities and neighborhood
```{r}
price_neighbor = df_175 %>%
  group_by(neighbourhood) %>%
  summarise_at(vars(price), list(price = mean))

price_neighbor = data.frame(price_neighbor)

price_neighbor[order(-rank(price_neighbor$price), decreasing = FALSE), ]%>% 
  kbl() %>%
  kable_paper("hover", full_width = F)
```

```{r}
rating_neighbor = df_175 %>%
  group_by(neighbourhood) %>%
  summarise_at(vars(review_scores_rating), list(review_scores_rating = mean))

rating_neighbor = data.frame(rating_neighbor)
#rating_neighbor
rating_neighbor[order(-rank(rating_neighbor$review_scores_rating), decreasing = FALSE), ]%>% 
  kbl() %>%
  kable_paper("hover", full_width = F)
```

```{r}
amenities_neighborhood = df_175 %>%
  group_by(neighbourhood) %>%
  summarise_at(vars(amenities), list(amenities = mean))

amenities_neighborhood = data.frame(amenities_neighborhood)

amenities_neighborhood[order(-rank(amenities_neighborhood$amenities), decreasing = FALSE), ]%>% 
  kbl() %>%
  kable_paper("hover", full_width = F)
```


# SMART Questions

## What neighbourhood has the best value?

To find the neighborhood that has the best AirBnB for rating and price, we will compare the mean price vs. mean rating for our 10 neighborhoods. 

First, we will run an ANOVA to see if there is any significant difference between the price and rating averages across neighborhoods, then we will graph and select our best neighborhood selection. 

```{r}

#anova test to compare mean price
anovaRes_price1 <-  aov(price ~ neighbourhood, data=df_175)
xkabledply(anovaRes_price1, title = "Price by Neighborhood ANOVA")

#anova test to compare mean rating
anovaRes_rating1 <-  aov(review_scores_rating ~  neighbourhood, data=df_175)
xkabledply(anovaRes_rating1, title = "Rating by Neighborhood ANOVA")

```
What we find in both of these Anova results is that there is a significant difference between average price and rating by neighborhood. We will use this knowledge to assume there must be a DC neighborhood with the better prices/ratings than others. 

```{r}
#create mean columns in dataframe

means_df <- df_175 %>%
  group_by(neighbourhood_short,neighbourhood) %>%
  summarise_at(vars(c(price,review_scores_rating, Freq, latitude,longitude)), funs(mean(., na.rm=TRUE)))

means_df_rt <- df_175 %>%
  group_by(neighbourhood_short,neighbourhood,room_type) %>%
  summarise_at(vars(c(price,review_scores_rating, Freq, latitude,longitude)), funs(mean(., na.rm=TRUE)))

ggplot(means_df) + geom_point(aes(x=review_scores_rating, y=price, colour=neighbourhood_short),size=4)+ theme(axis.text.x = element_text(angle = 90),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        legend.title=element_text(size=9),
        plot.title = element_text(color="black", face="bold", size=16, hjust=0),
        panel.grid.major = element_line(colour = "grey90", size = 0.2),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = 'white'),
        legend.position="right")+
        labs(colour = "Neighborhood", x="Mean Rating", y="Mean Price")+
        ggtitle("Mean Price by Mean Rating for DC Neighborhoods")+ geom_hline(yintercept=mean(means_df$price), linetype="dashed", color = "red")+
   geom_vline(xintercept=mean(means_df$review_scores_rating), linetype="dashed", color = "red")

means_df_select <- means_df[which(means_df$price<mean(means_df$price) & means_df$review_scores_rating > mean(means_df$review_scores_rating)),]

#id for neighborhoods
means_df_select$ID <- seq.int(nrow(means_df_select))

means_df_select[c(8,2:4)]%>% 
  kbl() %>%
  kable_paper("hover", full_width = F)

```

We find that we have `r nrow(means_df_select)` neighborhoods to suggest to our friend where the overall AirBnB price is less than DC's averaEntire home/aptge and where the rating is greater than DC's average. We can map these out below. 

```{r}
pal1 <- colorFactor(c("#72B000","#00BFC4","#7997ff"), domain = c("Columbia Height", "Edgewood, Bloom", "Kalorama Height"))


# create leaflet map 

map <- leaflet(means_df_select) %>%
  addTiles() %>%
  addCircleMarkers(lng = ~longitude,
                   lat = ~latitude, 
                   radius=~sqrt(Freq),
                   color=~pal1(neighbourhood_short),
                   label=~ID,
                   labelOptions = labelOptions(noHide = T, textOnly = T, textsize = "7px",direction = 'center',style = list(
        "color" = "white")),
                   stroke = FALSE, 
                   fillOpacity = 0.7)%>%
  addLegend("bottomright",pal = pal1, values = ~means_df_select$neighbourhood_short, opacity = 1, title = "Room Type")


map %>%  addProviderTiles(providers$CartoDB.Positron)



```

This is helpful, but we should probably include room type to help our friend know if there is a room type/neighboorhood combination that would be the rest to search for. 

Let's run an anova to see if there is a significant difference between mean price and mean rating by room type.

```{r}
#anova test to compare mean price
anovaRes_price2 <-  aov(price ~ room_type, data=means_df_rt)
xkabledply(anovaRes_price2, title = "Price ANOVA")

#anova test to compare mean rating
anovaRes_rating2 <-  aov(review_scores_rating ~ room_type, data=means_df_rt)
xkabledply(anovaRes_rating2, title = "Rating ANOVA")
```
What we find is that for price, room type is something to consider as there are significant differences between the mean prices. However, rating is not as much of a comparative factor when determining a room type to select on AirBnB as there is no significant differences between the mean.

We will show our friend an analysis where we look for the best true values by room type where the AirBnBs have a price lower than the mean and rating higher than the mean. However, rating should not be considered when choosing between different room types.

```{r}

means_df_rt_eha <- means_df_rt[which(means_df_rt$room_type=="Entire home/apt"),]

means_df_rt_pr <- means_df_rt[which(means_df_rt$room_type=="Private room"),]

means_df_rt_sr <- means_df_rt[which(means_df_rt$room_type=="Shared room"),]

means_df_rt_hr <- means_df_rt[which(means_df_rt$room_type=="Hotel room"),]


ggplot(means_df_rt) + geom_point(aes(x=review_scores_rating, y=price, colour=neighbourhood_short, shape=room_type),size=4, alpha=.85)+  scale_shape_manual(values=c(21,22,23,24))+
  theme(axis.text.x = element_text(angle = 90),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9),
        legend.title=element_text(size=9),
        plot.title = element_text(color="black", face="bold", size=16, hjust=0),
        panel.grid.major = element_line(colour = "grey90", size = 0.2),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = 'white'),
        legend.position="right")+
        labs(colour = "Neighborhood", x="Mean Rating", y="Mean Price")+
        ggtitle("Mean Price by Mean Rating in DC Neighborhoods")+ geom_hline(yintercept=mean(means_df_rt_eha$price), linetype="dashed", color = "#51c5ed")+
        annotate("text", x=2.7, y=(mean(means_df_rt_eha$price)+8), label="Entire home/apt avg", color = "#51c5ed",size=3)+
        geom_vline(xintercept=mean(means_df_rt_eha$review_scores_rating), linetype="dashed", color = "#51c5ed")+       
        geom_hline(yintercept=mean(means_df_rt_pr$price), linetype="dashed", color = "#C3EB78")+ 
        annotate("text", x=2.6, y=(mean(means_df_rt_pr$price)+8), label="Private room avg", color = "#C3EB78",size=3)+
        geom_vline(xintercept=mean(means_df_rt_pr$review_scores_rating), linetype="dashed", color = "#C3EB78")+
        geom_hline(yintercept=mean(means_df_rt_sr$price), linetype="dashed", color = "#ff616f")+
        annotate("text", x=2.6, y=(mean(means_df_rt_sr$price)+8), label="Shared room avg", color = "#ff616f",size=3)+
        geom_vline(xintercept=mean(means_df_rt_sr$review_scores_rating), linetype="dashed", color = "#ff616f")+
        geom_hline(yintercept=mean(means_df_rt_hr$price), linetype="dashed", color = "#3D348B")+
        annotate("text", x=2.6, y=(mean(means_df_rt_hr$price)+8), label="Hotel room avg", color = "#3D348B",size=3)+
        geom_vline(xintercept=mean(means_df_rt_hr$review_scores_rating), linetype="dashed", color = "#3D348B")


means_df_rt_eha_select <- means_df_rt_eha[which(means_df_rt_eha$price<mean(means_df_rt_eha$price) & means_df_rt_eha$review_scores_rating > mean(means_df_rt_eha$review_scores_rating)),]

means_df_rt_pr_select <- means_df_rt_pr[which(means_df_rt_pr$price<mean(means_df_rt_pr$price) & means_df_rt_pr$review_scores_rating > mean(means_df_rt_pr$review_scores_rating)),]

means_df_rt_sr_select <- means_df_rt_sr[which(means_df_rt_sr$price<mean(means_df_rt_sr$price) & means_df_rt_sr$review_scores_rating > mean(means_df_rt_sr$review_scores_rating)),]

means_df_rt_hr_select <- means_df_rt_hr[which(means_df_rt_hr$price<mean(means_df_rt_hr$price) & means_df_rt_hr$review_scores_rating > mean(means_df_rt_hr$review_scores_rating)),]

means_df_rt_select <- rbind(means_df_rt_eha_select,means_df_rt_pr_select,means_df_rt_sr_select,means_df_rt_hr_select)
```

```{r}

#id for neighborhoods
means_df_rt_select$ID <- seq.int(nrow(means_df_rt_select))

means_df_rt_select[c(9,2:5)]%>% 
  kbl() %>%
  kable_paper("hover", full_width = F)
```

Now we can map by room type suggestions

```{r}
#color palette

pal2 <- colorFactor(c("#51c5ed","#C3EB78","#ff616f","#3D348B"), domain = c("Entire home/apt","Shared room","Private room","Hotel room"))




# create leaflet map 

map2 <- leaflet(means_df_rt_select) %>%
  addTiles() %>%
  addCircleMarkers(lng = ~longitude,
                   lat = ~latitude, 
                   radius=~sqrt(Freq),
                   color=~pal2(room_type),
                   label=~ID,
                   labelOptions = labelOptions(noHide = T, textOnly = T, textsize = "7px",direction = 'center',style = list(
        "color" = "white")),
                   stroke = FALSE, 
                   fillOpacity = 0.6)%>% 
addLegend("bottomright",pal = pal2, values = ~means_df_rt_select$room_type, opacity = 1, title = "Room Type")

map2 %>%  addProviderTiles(providers$CartoDB.Positron)



```


## Do names of listings affect reviews and price?

All listings try to keep catchy and attractive names to get clicks by prospective guests. We want to investigate whether names with certain characteristics are better or worse than others.

```{r}

data(stop_words)

corpus <- df %>% select(id, name) %>%
  unnest_tokens(word, name) %>% filter(!word %in% stop_words$word, str_detect(word, "[a-z]"))

all_words <- corpus %>% group_by(word) %>% dplyr::summarise(count = n())

wordcloud(words = all_words$word, freq = all_words$count, , min.freq = 50, colors=brewer.pal(8, "Dark2"))
```


The wordcloud shows that certain key words such as metro, basement, private, townhouse, metro etc are present in a lot of listings.

```{r}
df_corpus <- corpus %>% left_join(df)
corpus_agg <- df_corpus %>% 
  group_by(word) %>% 
  dplyr::summarise(avg_rating = mean(review_scores_rating), avg_price = mean(price), count = n()) %>% 
  filter(count > 150)

ggplot(corpus_agg, aes(x=avg_rating, y=avg_price)) + geom_text(label=corpus_agg$word, aes(size=count, color = word)) + scale_size_continuous(range = c(2, 10)) + guides(color=FALSE)

```

* Cozy places are cheaper but worse than spacious ones.
* Houses are pricier than condos with no difference in ratings. 
* Parking places are more expensive than those near a metro, with no difference in ratings.
* Historic places are the best rated.
